Do I Need to Model You in order to Learn With You?

### 2015-04-22 mutual-modeling.tex
Switched to Springer style (for Journal of CSCL)

\documentclass[twocolumn]{article}

@@

\usepackage[round]{natbib}

@@

\title{Do I Need to Model You in order to Learn With You?}

\author{
    Pierre Dillenbourg, Séverin Lemaignan \\
    \small Computer-Human Interaction in Learning and Instruction (CHILI) \\
    \small Ecole Polytechnique Fédérale de Lausanne (EPFL) \\
    \small CH-1015 Lausanne, Switzerland \\
    {\tt firstname.lastname@epfl.ch}
    \and
    Mirweis Sangin \\
    \and
    Nicolas Nova \\
    \small Haute Ecole Arts \& Design de Genève\\
    {\tt nicolas.nova@hesge.ch}
    \and
    René Glaus
    \and
    Gaëlle Molinari \\
    \small Fernuni Schweiz \\
    {\tt gaelle.molinari@fernuni.ch}
}
\begin{document}
\maketitle

\listoffixmes

@@

From its very beginning, CSCL research has been following
\citet{roschelle1995construction} suggestion that collaborative learning has
something to do with the process of constructing and maintaining a \emph{shared
understanding} of the task at hand. Building a shared/mutual understanding
refers to the upper class of collaborative learning situations, those in which
students should build upon each other's understanding to refine their own
understanding: what is expected to produce learning is not the mere fact that
two students build the same understanding but the cognitive effort they have to
engage to build this shared understanding~\citep{schwartz1995emergence}. This
effort can be observed by the frequency of rich interactions, \ie interactions
whose occurrence has been related to learning: (self-) explanations in cognitive
science~\cite{chi1989self, webb1991task}, conflict resolution in
socio-cognitive theories~\cite{doise1975social},
mutual regulation~\cite{blaye1995collaborative} in a Vygostkian perspective, etc. The
construction of a shared understanding has been investigated for several years
in psycholinguistics, under the  notion of
\emph{grounding}~\citep{clark1986referring}. However, the relevance of grounding
mechanisms for explaining learning outcomes has been questioned in learning
sciences. The monitoring and repair of misunderstanding explains for instance
referential failures in short dialogue episodes but does hardly predict
\emph{conceptual change} (\ie the acquisition, acceptation and integration of a
new belief into one's mental model\fxnote{check with Pierre}) over longer
sessions~\cite{dillenbourg2006sharing}. The cumulative effect of grounding
episodes can probably be better understood from a socio-cultural perspective:

@@

\begin{figure*}
    \centering
    \begin{tikzpicture}[scale=0.8]
        \node[anchor=south west,inner sep=0] at (0,0)
            {\includegraphics[width=0.65\textwidth]{image10.png}};

            \node[rectangle,draw, thick] at (11,6.2) {Self map};
            \node[rectangle,draw, thick] at (11,3) {Partner map};
            \node[rectangle,draw, thick] at (3,2) {Collaborative map};
    \end{tikzpicture}
    \caption{The group concept map and the individual concept maps in study
    4}
    \label{study4:concept_map}
\end{figure*}

@@

\section*{Acknowledgments}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{plainnat}
\bibliography{biblio}

>>>>

\documentclass[natbib]{svjour3}

@@

@@

\title{Do I Need to Model You in order to Learn With You?}
\subtitle{Mutual Modelling in CSCL}

\author{
    Pierre Dillenbourg
    \and
    Séverin Lemaignan
    \and
    Mirweis Sangin
    \and
    Nicolas Nova
    \and
    René Glaus
    \and
    Gaëlle Molinari
}
\institute{
    Pierre Dillenbourg, Séverin Lemaignan \at Computer-Human Interaction in Learning and Instruction \\
    École Polytechnique Fédérale de Lausanne (EPFL) \\ CH-1015 Lausanne, Switzerland \\
    \email{firstname.lastname@epfl.ch}
    \and
    Mirweis Sangin \at Sony Computer Entertainment Europe
    \and
    Nicolas Nova \at Haute École Arts \& Design de Genève \\\email{nicolas.nova@hesge.ch}
    \and
    René Glaus
    \and
    Gaëlle Molinari \at Fernuni Schweiz \\\email{gaelle.molinari@fernuni.ch}
}
\begin{document}
\maketitle

@@

From its very beginning, CSCL research has been following
\citet{roschelle1995construction} suggestion that collaborative learning has
something to do with the process of constructing and maintaining a \emph{shared
understanding} of the task at hand. Building a shared/mutual understanding
refers to the upper class of collaborative learning situations, those in which
students should build upon each other's understanding to refine their own
understanding: what is expected to produce learning is not the mere fact that
two students build the same understanding but the cognitive effort they have to
engage to build this shared understanding~\citep{schwartz1995emergence}. This
effort can be observed by the frequency of rich interactions, \ie interactions
whose occurrence has been related to learning: (self-) explanations in cognitive
science~\citep{chi1989self, webb1991task}, conflict resolution in
socio-cognitive theories~\citep{doise1975social},
mutual regulation~\citep{blaye1995collaborative} in a Vygostkian perspective, etc. The
construction of a shared understanding has been investigated for several years
in psycholinguistics, under the  notion of
\emph{grounding}~\citep{clark1986referring}. However, the relevance of grounding
mechanisms for explaining learning outcomes has been questioned in learning
sciences. The monitoring and repair of misunderstanding explains for instance
referential failures in short dialogue episodes but does hardly predict
\emph{conceptual change} (\ie the acquisition, acceptation and integration of a
new belief into one's mental model\fxnote{check with Pierre}) over longer
sessions~\cite{dillenbourg2006sharing}. The cumulative effect of grounding
episodes can probably be better understood from a socio-cultural perspective:

@@

\begin{figure*}
    \centering
    \begin{tikzpicture}[scale=0.8]
        \node[anchor=south west,inner sep=0] at (0,0)
            {\includegraphics[width=0.75\textwidth]{image10.png}};

            \node[rectangle,draw, thick] at (10,5.4) {Self map};
            \node[rectangle,draw, thick] at (7.5,3.3) {Partner map};
            \node[rectangle,draw, thick] at (2.5,1.5) {Collaborative map};
    \end{tikzpicture}
    \caption{The group concept map and the individual concept maps in study
    4}
    \label{study4:concept_map}
\end{figure*}

@@

\begin{acknowledgements}

@@

\end{acknowledgements}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{spbasic}
\bibliography{biblio}
